Data Preparation

### 2019-01-09 Data Preparation.Rmd

### Course Manuals
To expand our topic modeling of course content, we would like to analyse the material in the course manuals. The `corpus_manuals` contains the pdfs of the course manuals for the year 2017-2018 (most recently, available).
```{r}
corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
                 readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```
## Student Data
The tibble `transcripts` contains the transcripts of a selection of `7` alumni students from the college[^2]. `transcripts` contains information on each course taken by each student such as the receives grade, the semester in which teh course was taken as well as the calendar year.
```{r transcripts}
transcripts <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1kj7tlfJAoN0F7IdoS3saT-2iC3nuDLwnDItNtCKoZ4k/edit#gid=936718979')
print(transcripts)
```

@@

```{r}
manuals_tokens <- manuals_td %>%
  select(id,text) %>%
  mutate(Concentration= substring(id, 1, 3), Code= substring(id,1,7))%>%
  unnest_tokens(word, text)
```

>>>>

### Course Manuals
To expand our topic modeling of course content, we would like to analyse the material in the course manuals. The `corpus_manuals` contains the pdfs of the course manuals for the year 2017-2018 (most recently, available).
```{r}
corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
                 readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```
## Student Data
The tibble `transcripts` contains the transcripts of a selection of `7` alumni students from the college[^2]. `transcripts` contains information on each course taken by each student such as the receives grade, the semester in which teh course was taken as well as the calendar year.
```{r transcripts}
transcripts <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1kj7tlfJAoN0F7IdoS3saT-2iC3nuDLwnDItNtCKoZ4k/edit#gid=936718979')
print(transcripts)
```
COMMENT SOFIA: save a_clean_transcript as d_transcript

ALL OTHER STUDENTS:
The data we will be using was provided in two documents with the same format. We import them, merge them and remove duplicate rows.

```{r Data Import}
t1 <- read.csv("Raw Grades/grades1.csv",na.strings=c("","NA"))
t2 <- read.csv("Raw Grades/grades2.csv",na.strings=c("","NA"))
d_dirt <-rbind(t1, t2)
d_dirt <- d_dirt[!duplicated(d_dirt),] #could use distinct() from dplyr
```

@@

```{r}
manuals_tokens <- manuals_td %>%
  select(id,text) %>%
  mutate(Concentration= substring(id, 1, 3), Code= substring(id,1,7))%>%
  unnest_tokens(word, text)
```
###(Optional) Pre-processing Course Manuals- Removing stopwords
Some characters appear with sufficient frequency to be relevant but not often enough accross all courses to be deleted when using tf-idf (see sections bellow), it is therefore convenient to add some stopwords and remove numbers. For this we import stop_words from tidytext, and search all our words with grep for stand alone numbers. We save these words in different dataframes and then exclude with an antijoin.
```{r}

data("stop_words")  #imports common stopwords

my_stop_words <- data.frame (word = c(1:11, "students", "______________________________________________________________________________")) #no stemming ("students")
number_stopwords <- number_stopwords <- manuals_tokens %>% #can be cleaner by using unique (?)
  mutate(is_number=grepl("^[-]{0,1}[0-9]{0,}.{0,1}[0-9]{1,}$",word))%>% #finds stand alone numbers (incl. -, and .)
  filter(is_number==T)

manuals_tokens_preprocessed <- manuals_tokens %>%
  anti_join(stop_words)     %>%
  anti_join(my_stop_words) %>%
  anti_join(number_stopwords, by = c("word"="word"))

```
